Predicting the Ending Notes of Bach Chorales

### 2018-04-17 Paper.tex
Completed computer model

This model predicted the endings of a total of 56 chorales correctly. While the number of over-estimations was reduced by around 60\%, there was a 50\% rise in the number of underestimations. The minimal improvement of the model would suggest that the patterns created for this model were either incorrect or insufficiently described the musical patterns. In any case, there is much room for improvement for this model.

\subsection{Computer Model}
In the final model, each note of the chorale was analyzed separately, then given a probability of that pitch being the same note as the final note. The 70 random chorales from the data set were used as the training set, with the remaining 30 chorales left for testing.

>>>>

This model predicted the endings of a total of 56 chorales correctly. While the number of overestimations was reduced by around 60\%, there was a 50\% rise in the number of underestimations. The minimal improvement of the model would suggest that the patterns created for this model were either incorrect or insufficiently described the musical patterns. In any case, there is much room for improvement for this model.

\subsection{Computer Model}
In the final model, each chorale was used in a decision tree to predict the final pitch. 70 random chorales from the data set were used as the training set, with the remaining 30 chorales left for testing. This model was able to correctly predict between 62 and 75 of the 100 chorales.
